---
title: "Public library"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Public library}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(c2z)
```

"I think the health of our civilization, the depth of our awareness about the 
underpinnings of our culture and our concern for the future can all be tested 
by how well we support our libraries" (Sagan, 1980, p. 282).

I love libraries. I also love meta-libraries. There currently exists no adequate
way to browse public Zotero libraries, however, you may search groups at the 
Zotero [website](https://www.zotero.org/search/type/group).

In the following example we will harvest the items stored in such a public 
Zotero group. Also, please see the [magnificent vignette](articles/c2z_vignette.html) and 
other [documentation](https://oeysan.github.io/c2z/).

```{r example}
# Query public library
example <- Zotero(
  user = FALSE, 
  id = "4986462",
  api = NA,
  library = TRUE,
  index = TRUE
)
# Print index
example$index$name
``` 

# References

Sagan, C. (1980). *Cosmos*. Ballantine Books.

