---
title: "Behold c2z!"
bibliography: '`r gsub("\\\\", "/", file.path(tempdir(), "references.bib"))`'
csl: '`r gsub("\\\\", "/", file.path(tempdir(), "style.csl"))`'
lang: "en-US"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The following vignette will demonstrate the basic functionality (i.e., awesome 
might) of *`c2z`*. 

```{r setup}
library(c2z)
```

# Collections

Your computer desktop reveals your 
[D&D alignment](https://www.pcgamer.com/pcg-staff-desktop-dnd-alignment-chart/).
Similarly, the way you structure your Zotero library through collections 
reveals your personality. (Chaotic neutral is not using collections, obviously.)

*`c2z`* lets you create nested collections on a whim, as seen below.

## Creating collections

In this example we define a vector of nine elements based on "the quick brown 
fox jumps over the lazy dog". We use the `Zotero` function, a wrapper that 
connects with the Zotero API and combines all major functions in *`c2z`*, to 
create nine nested collections based on the string  (i.e., "dog" nested in 
"lazy" nested in "the" et cetera). We set `library = TRUE`, thereby querying 
the Zotero library, and `create = TRUE` to create any collections that does not 
exist (i.e., all nine collections). 

This is a recursive action, so let's keep the noise at a minimum and set 
`silent = TRUE`.

```{r create.collections, eval = TRUE}
# Let's create a vector of nested collections
collection.names <- c(
  "The", "quick", "brown", "fox", "jumps", "over", "the", "lazy", "dog"
  )

# Create the collections
create.collections <- Zotero(
  collection.names = collection.names,
  library = TRUE,
  create = TRUE,
  silent = TRUE
)
```

## Using collections

Now that we have created some collections, we can access the collections in
different ways. By default, the function will find the last element in the vector 
(i.e., "dog").

```{r find.dog, eval = TRUE}
# Dog
create.collections$collections  |>
  dplyr::select(c(key, name, parentCollection))
```

However, we often want access all, or some, nested collections. We can achieve 
this using two different approaches. 1) using `recursive = TRUE` to access the 
given element and then recursively find the nested collections, or 2) using 
`ancestor = TRUE` and trace the lineage of the specified collection.

You may use `collection.name` (you don't have several top-level collections 
with the same name, do you? If so, the function will select the newest 
collection with the specified name), or `collection.key` if you keep track of
such things. *`c2z`* will by default look for collections names regardless of 
letter case, and if this is important set `case.insensitive = FALSE`.

### All collections

```{r find.collections, eval = TRUE}
# Find collections
collections <- Zotero(
  collection.names = "The",
  recursive = TRUE,
  library = TRUE,
  silent = TRUE
)

# print collections
collections$collections |>
  dplyr::select(c(key, name, parentCollection))
```

### Recursive path

```{r recursive, eval = TRUE}
# Find collections
recursive <- Zotero(
  collection.names = c("The", "quick", "brown"),
  recursive = TRUE,
  library = TRUE,
  silent = TRUE
)

# print collections
recursive$collections |>
  dplyr::select(name)
```

### Ancestor path

```{r ancestor, eval = TRUE}
# Find collections
ancestor <- Zotero(
  collection.names = c("The", "quick", "brown", "fox"),
  ancestor = TRUE,
  library = TRUE,
  silent = TRUE
)

# print collections
ancestor$collections |>
  dplyr::select(name)
```

# Items

Okay, so we've created a bunch of collections. Kinda cool, I guess? But 
collections are somewhat pointless without items. Sooo, lets add some items!

## Adding items from Cristin

One motivation to develop *`c2z`* is an attempt at making registering data at 
Cristin feel useful. The following example of the `Cristin` function will 
gather all publications containing the word "cheese", published since 2020 
(it was a good year for cheese, probably). 

The `zotero.import` is set to `TRUE`, indicating that the function will use 
`CristinWrangler` to convert Cristin metadata into an acceptable format for
Zotero. `use.identifiers = TRUE` and the function will therefore use any
identifiers (i.e., ISBN or DOI) to augment the metadata. Furthermore, 
`crossref.search = TRUE`, meaning that the function will search CrossRef for 
metadata if identifiers are missing. Also, `autosearch = TRUE` and the process 
is consequently conducted automatically. The items are posted to the Zotero 
library using `Zotero`, where items are uploaded using the `items` argument. 
The `index = TRUE`, creating an index of the items.

Please note that `crossref.search` should normally not be used (see the 
[README](https://oeysan.github.io/c2z/)). 

Rather than finicking over h-indexes and impact factors, Norwegians have a 
weird obsession with NVI (Norwegian Science Index), which is a two-level
index where level one publications are ordinary and level two are great 
(it probably makes sense). However, Cristin has no simple method of filtering
out publications that qualify for the two levels. 

The specified `filter` arguments try to filter out categories that usually 
contain publications that are worthy of the NVI (see all the Cristin 
[categories](https://api.cristin.no/v2/results/categories?lang=en)).

Let's post the results to the collection "fox", while using the argument 
`get.items = FALSE` as not to add any items in the collection to the Zotero 
list. 

```{r cristin, eval = TRUE}
# Filter items
cristin.filter <- c(
  "ACADEMICREVIEW",
  "ARTICLEJOURNAL",
  "ARTICLE", 
  "ANTHOLOGYACA", 
  "CHAPTER", 
  "CHAPTERACADEMIC",
  "CHAPTERARTICLE",
  "COMMENTARYACA",
  "MONOGRAPHACA"
)

# Query Cristin
cristin <- Cristin(
  title = "cheese",
  published_since = 2020,
  published_before = 2021,
  filter = cristin.filter,
  zotero.import = TRUE,
  use.identifiers = TRUE,
  crossref.search = TRUE,
  autosearch = TRUE,
  silent = FALSE
)

# Get the fox key
fox <- collections$collections |> 
  dplyr::filter(name == "fox") |> 
  dplyr::pull("key")

# Post the items to the collection called fox
post.cristin <- Zotero(
  collection.key = fox,
  metadata = cristin$results,
  library = TRUE,
  index = TRUE,
  post = TRUE,
  post.collections = FALSE,
  post.items = TRUE,
  silent = TRUE
)

# Select only names in index and print
post.cristin$index |> 
  dplyr::select(name) |>
  print(width = 80)
```

In this second example we have decided that 2019 was an even better year for 
cheese and change the `published_since` argument to 2019. The reason why we
are doing this is to demonstrate the duplicate function in `Cristin`, 
which will identify any Cristin references imported into Zotero if 
`zotero.check = TRUE`.  The function will try to use the `zotero` argument 
to search the specified collection(s).

```{r cristin.check, eval = TRUE}
# Query Cristin (again)
cristin2 <- Cristin(
  title = "cheese",
  published_since = 2019,
  published_before = 2021,
  filter = cristin.filter,
  zotero.import = TRUE,
  zotero.check = TRUE,
  use.identifiers = FALSE,
  zotero = post.cristin
)
```

## Adding items from identifiers

Sometimes, it happens to everybody, we're having a bunch of ISBNs and DOIs 
lying around. Luckily, we can easily add them to Zotero using the `Zotero` 
wrapper. In this case we are adding them to the collection "quick".

```{r identifiers, eval = TRUE}
# ISBN
isbn.items <- c("9780761973836", "9788215048451")

# DOI
doi.items <- c("https://doi.org/10.31234/osf.io/venu6", 
               "10.1177/1098214010376532")

# Post the items to the collections called quick
identifiers <- Zotero(
  collection.names = c("The", "quick"),
  isbn = isbn.items,
  doi = doi.items,
  library = TRUE,
  index = TRUE,
  post = TRUE,
  post.collections = FALSE,
  post.items = TRUE,
  silent = TRUE,
  get.items = FALSE
)

# Select only names in index and print
identifiers$index |> 
  dplyr::select(name) |>
  print(width = 80)
```

## Adding items from the Man

When working in academia within a Norwegian context, you will frequently need 
to examine the musings of politicians, or their selected group of researchers. 
So, let's add some random white papers and official reports using `ZoteroGov`.

```{r gov, eval = TRUE}
# Combine to a single tibble using dplyr
gov.items <- dplyr::bind_rows(
  # Find some random white papers
  ZoteroGov(c("26 (2001-2002)", "31 (2014-2015)"), type = "meldst")$data,
  # Finds some random official Norwegian reports.
  ZoteroGov(c("2014: 4", "2018: 2"), type = "nou")$data
)

# Post the items to the collection called brown
## Fitting given the source
the.man <- Zotero(
  collection.names = c("The", "quick", "brown"),
  metadata = gov.items,
  library = TRUE,
  index  = TRUE,
  post = TRUE,
  post.collections = FALSE,
  post.items = TRUE,
  silent = TRUE,
  get.items = FALSE
)

# Select only names in index and print
the.man$index |> 
  dplyr::select(name) |>
  print(width = 80)
```

## Adding items from CRAN

Show some love (citations are love, yes?) for the authors that create
the packages that you use! (We see you, Hadley Wickham).

Here, we're using the `ZoteroCran` function to collect metadata from The 
Comprehensive R Archive Network (CRAN). The `collection.key` is defined as:

```{r lazy, eval = TRUE}
lazy <- collections$collections |> 
  dplyr::filter(name == "lazy") |> 
  dplyr::pull("key")
```

The key is "`r lazy`" and the argument `recursive = TRUE`, thus the function is 
looking for the specified collection (i.e., "lazy") and all its children
(i.e., "dog"). 

It is often useful to link items to several (nested) collections. For instance, 
you can create the nested collections "project -> CRAN-packages" and link the 
items to both collections. You can then choose to access all items under 
"project", including those in "CRAN-packages", or just access those filed under 
the latter.

```{r cran, eval = TRUE}
# Find selected packages 
packages <- c(
  "dplyr",
  "httr",
  "jsonlite",
  "purrr",
  "rvest",
  "rlang",
  "tibble",
  "tidyr",
  "tidyselect"
)

# Post the items to the collections called lazy and dog
cran <- Zotero(
  collection.key = lazy,
  metadata = ZoteroCran(packages)$data,
  library = TRUE,
  index = TRUE,
  recursive = TRUE,
  post = TRUE,
  post.collections = FALSE,
  post.items = TRUE,
  silent = FALSE,
  get.items = FALSE
)

# What do we got?
# Select only names in index and print
index <- cran$index |> 
  dplyr::select(name) |>
  print(width = 80)
```

# Copying

There are many situations where we want to copy collections and items 
(and attachments) between libraries. You may want to copy from a public Zotero
library to your own or share your collections with a research group.

The `Zotero` function contains a (somewhat convoluted) method of copying 
collections and items from a group library to a user library (and vice versa).
However, in this example we're appending the group collections to our long line
of nested collections, making the process somewhat messy. Therefore, we split
up the process using the `ZoteroCopy` and `ZoteroPost` functions. The 
`change.library` argument will query `Zotero` and alter the location according
to specified coordinates (the default location is the user library as defined in 
`.Renviron`).

Please see the [tutorial](articles/zotero_api.html) on how to set up user/group 
id and API keys.

```{r copy, eval = TRUE}
# Access the group library (defined in .Renviron)
group.library <- Zotero(
  user = FALSE,
  library = TRUE,
  silent = FALSE
)

# Copy the library creating new keys 
copy.library <- ZoteroCopy(
  zotero = group.library,
  change.library = TRUE,
  silent = FALSE
)

# Find key for dog
dog <- collections$collections |> 
  dplyr::filter(name == "dog") |> 
  dplyr::pull("key")

# Change parent collection of top-level collection to dog
copy.library$collections <- copy.library$collections |>
  dplyr::mutate(
    parentCollection = dplyr::case_when(
      parentCollection == "FALSE" ~ dog,
      TRUE ~ parentCollection
    )
  )

# Copy the collection and items to the user library
post.copy <- ZoteroPost(
  zotero = copy.library,
  silent = TRUE
)

# Select only names in index and print
ZoteroIndex(post.copy$items) |>
  dplyr::select(name) |>
  print(width = 80)
```

# Bibliography

It's a wrap! 

Now it's time to harvest the bounty that we have created during the
steps above. We could create separate bibliographies, but for the sake of 
simplicity we are mashing it all together. That's friendship! 

The arguments used in `Zotero` are somewhat self-explanatory, however, we are 
also `csl.type` to access a 
[style repository](https://github.com/citation-style-language/styles) in order 
to create a Citation Style Language (CSL) file according to 
[APA7](https://apastyle.apa.org/).

```{r bibliography, eval = TRUE, cache = FALSE}
# Create references.bib in biblatex format with style.csl according to APA7
bibliography <- Zotero(
  collection.names = "The",
  recursive = TRUE,
  library = TRUE,
  export = TRUE,
  format = "biblatex",
  save.data = TRUE,
  save.path = tempdir(),
  bib.name = "references",
  csl.type = "apa-single-spaced",
  csl.name = "style",
  silent = TRUE
)

# What do we got?
sprintf(
  "We now have %s collections, %s references, and %s attachments",
  bibliography$n.collections,
  bibliography$n.items,
  bibliography$n.attachments
)
```

# Deleting

Housecleaning! We should clean up the mess in your library. You could set 
[`ragnarok`](https://www.youtube.com/watch?v=iEV3mbS-HgY) and `force = TRUE`, 
if you want to delete everything in your library.

```{r deleting, eval = TRUE}
# Delete all collections and items belonging to initial key
delete <- ZoteroDelete(
  bibliography, 
  delete.collections = TRUE,
  delete.items = TRUE
)
```


# References

We can now display the references that we have collected and created using 
*`c2z`*.

---
nocite: '@*'
---
